Measuring contrast processing in the visual system using SSVEP

### 2024-04-27 review.qmd
Updated references

where $C_\mathrm{mask}$ reflects the contrast of the mask component at a distinct frequency from that of the target. The effect of this extra term is to reduce the target response (see right panel of @fig-twoinputs). For a linear contrast axis, the contrast response function becomes shallower, whereas on a logarithmic contrast axis it maintains its steepness and shifts to the right. Suppressive effects of this kind have been obtained using SSVEP with a variety of different types of mask, including orthogonal overlaid masks, surround masks, and dichoptic masks [for a meta-analysis see @Baker2021].

@@

Attention exerts a profound influence on visual performance: For example, allowing people to attend covertly to a spatial location for example, improves their performance on a target detection task significantly (Posner, https://pubmed.ncbi.nlm.nih.gov/11934448/, https://pubmed.ncbi.nlm.nih.gov/10788636/,  (Morrone, Denti, & Spinelli,
2004; Pestelli, Ling, & Carrasco, 2009) , [@bashinski1980enhancement]).

In principle, this enhancement may be driven both by modulation of the underlying signal or noise characteristics, or by additional decision-theoretic factors such as reduction in spatial uncertainty (https://jov.arvojournals.org/article.aspx?articleid=2121966, https://jov.arvojournals.org/article.aspx?articleid=2192826).

@@

SSVEP and psychophysical measurements of attentional effects on both luminance and chromatic contrast strongly implicated gain control an an underlying mechanism [@DiRusso2001GainControl, @lu1998external].  In the late 2000s a comprehensive theoretical model for attentional modulation was developed that framed it as a gain control computation (Reynolds and Heeger 2009, Boynton Vis Res 2009). This framework has proven to be influential - explaining a wide range of phenomena from the earlier literature and demonstrating subtle interactions between the size of the attentional 'spotlight' and the stimulus configuration which rationalise many apparent contradictions in the literature. Subsequent papers   (effect of stimulus configuration critical). Then... talk about Lauriten et al, Verghese (2 papers) maybe mention Crognale / Highsmith, Wang+Wade and Jasna's paper from 2018. https://www.sciencedirect.com/science/article/abs/pii/S1053811918303860) Probably lots more Carasco ...

>>>>

where $C_\mathrm{mask}$ reflects the contrast of the mask component at a distinct frequency from that of the target. The effect of this extra term is to reduce the target response (see right panel of @fig-twoinputs). For a linear contrast axis, the contrast response function becomes shallower, whereas on a logarithmic contrast axis it maintains its steepness and shifts to the right. Suppressive effects of this kind have been obtained using SSVEP with a variety of different types of mask, including orthogonal overlaid masks, surround masks, and dichoptic masks [@Burr1987; @Ross1991; @Candy2001; @Busse2009; @Salelkar2020; @Cunningham2017; for a meta-analysis see @Baker2021].

@@

Attention exerts a profound influence on visual performance: For example, allowing people to attend covertly to a spatial location for example, improves their performance on a target detection task significantly [@Posner1980; @Cameron2002; @Carrasco2000; @Bashinski1980; @Morrone2004; @Pestilli2009].

In principle, this enhancement may be driven both by modulation of the underlying signal or noise characteristics, or by additional decision-theoretic factors such as reduction in spatial uncertainty [@Gould2007; @Petrov2006].

@@

Electrophysiological and psychophysical measurements of attentional effects on both luminance and chromatic contrast strongly implicated gain control an an underlying mechanism [@DiRusso1999; @DiRusso2001; @Lu1998] and demonstrated that these effects differed between chromatic and achromatic pathways [@DiRusso1999b].  In the late 2000s a comprehensive theoretical model for attentional modulation was developed that framed it as a gain control computation (Reynolds and Heeger 2009, Boynton Vis Res 2009). This framework has proven to be influential - explaining a wide range of phenomena from the earlier literature and demonstrating subtle interactions between the size of the attentional 'spotlight' and the stimulus configuration which rationalise many apparent contradictions in the literature. Subsequent papers   (effect of stimulus configuration critical). Then... talk about Lauriten et al, Verghese (2 papers) maybe mention Crognale / Highsmith, Wang+Wade and Jasna's paper from 2018. https://www.sciencedirect.com/science/article/abs/pii/S1053811918303860) Probably lots more Carasco ...
